\documentclass[11pt,letterpaper]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{setspace}
\onehalfspacing

\begin{document}
	
%	\noindent [Your Name]  \\
%	[Your Address]  \\
%	[City, Postal Code]  \\
%	[Email Address]  \\
%	[Phone Number]  \\
%	[Date]
%	
%	\vspace{1cm}
%	
%	\noindent To: [Legal Support Organization / Human Rights Advocate]  \\
%	[Their Address]  \\
%	[City, Postal Code]
	
	\vspace{1cm}
	
	\begin{center}
		\textbf{Subject: Legal Support Inquiry – Violation of Rights of Radu Briciu by the Romanian State and the Priory Hospital}
	\end{center}
	
	\vspace{0.5cm}
	
	To whom it may concern,
	
	I am writing to formally request legal assistance regarding the case of Radu Briciu, who has been subjected to forced medical treatment against his will, in violation of his fundamental human rights. The actions of the Romanian state and the Priory Hospital have raised serious legal and ethical concerns, including but not limited to medical coercion, violation of patient autonomy, and potential breaches of national and international legal standards.
	
	\section*{Background of the Case}
	\begin{enumerate}
		\item \textbf{Forced Medical Treatment} – Despite clear objections, Radu Briciu has been subjected to non-consensual administration of medication by medical authorities at the Priory Hospital.
		\item \textbf{Violation of Patient Rights} – The actions taken appear to disregard the rights enshrined in Romanian law and international conventions protecting individual autonomy and informed consent in medical treatment.
		\item \textbf{State Involvement and Systemic Failure} – The Romanian authorities have either facilitated or failed to prevent these violations, raising concerns of systemic abuse and disregard for human rights.
		\item \textbf{Psychological and Physical Harm} – The forced administration of medication has resulted in distress, unwanted side effects, and a significant infringement on personal dignity.
	\end{enumerate}
	
	\section*{Legal Concerns}
	\begin{itemize}
		\item Violation of \textbf{Article 3} (prohibition of inhuman or degrading treatment) and \textbf{Article 8} (right to respect for private life) of the European Convention on Human Rights.
		\item Violation of \textbf{Romanian Health Law No. 46/2003} on patient rights, which guarantees informed consent.
		\item Potential breaches of international medical ethics, including the \textbf{Universal Declaration on Bioethics and Human Rights}.
	\end{itemize}
	
	\section*{Request for Legal Assistance}
	Given the severity of these violations, I seek urgent legal assistance to:
	\begin{itemize}
		\item Challenge the forced medical treatment through legal avenues.
		\item Hold the responsible parties accountable.
		\item Ensure that Mr. Briciu's rights are fully respected moving forward.
		\item Explore possibilities for compensation or legal redress.
	\end{itemize}
	
	Please advise on the next steps to initiate legal proceedings or file a formal complaint with the appropriate human rights bodies. If necessary, I am willing to provide further documentation and statements supporting this case.
	
	I appreciate your prompt attention to this serious matter and look forward to your response.
	
	\vspace{1cm}
	
	Sincerely,  \\
	Radu Briciu
	
\end{document}

